---
title       : Reproducible Pitch Presentation
subtitle    : Ballon d'Or 2015 Vote Analysis
author      : Narendra Choudhary
job         : Developing Data Products Coursera Class (January 2016)
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, bootstrap]  # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---
## About this project
This project provides a comparison of votes casted for FIFA Ballon d'Or Men 2015. The data used is availabe at
[FIFA.com](http://www.fifa.com/ballon-dor/official-documents/index.html).  
A brief How-to is provided in application for those who aren't aware of FIFA Ballon d'Or voting procedure. FIFA uses preferential voting with points divided between ranks.
Application can handle 3 types of comparisons:
* First comparison type is "**All Players**". It displays a plot comparing all nominees. Options for selecting players which have collected votes within a range can also be selected using options.
* Second comparison type is "**Two Players**". Options are selecting two players. Any two nominees can be compared using this comparison type.
* Last comparison type is "**One Player**". Option allows choosing the players whose stats user wishes to know. A plot showing distribution of player's votes appear.

Selecting comparison type renders further option(s) available for that comparison type. Barplot (stacked/side-by-side) is generated based on comparison type and options. Color Coding has been used to differentiate voting choices (1st, 2nd and 3rd).

--- .class #id
## Data
```{r}
str(playerwise_men) # data frame of men votes
```
Next slide shows a snippet of `server.R` which generates dynamic UI.

--- .class #id
## Dynamic UI
```{r, eval=FALSE}
output$radioButtonControls <- renderUI({
        # Selects UI based on input type
        if(input$action_type == "one"){ # For one player option
            wellPanel(
                playerselect_block # selectInput Block
            )
        }else if(input$action_type == "two"){ # For two players option
            wellPanel(
                playercomparison1_block, # selectInput Block
                playercomparison2_block # selectInput Block
            )
        }else{ # For all players option
            wellPanel( # 3 sliderInput Blocks
                min_5pts, min_3pts, min_1pts
            )
        }
    })
```

---&twocol
## Plot: Examples

*** {name: left}

```{r echo=FALSE, error=FALSE, message=FALSE}
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(reshape2))
r_data <- filter(playerwise_men, player_name == "Messi Lionel" | player_name == "Cristiano Ronaldo") %>% melt() %>% filter(variable != "total")
ggplot(r_data, aes(x=player_name, y = value, fill=variable)) + 
        geom_bar(stat="identity", position = "dodge", color = "black") + 
        theme_bw() +
        theme(
            axis.text.x = element_text(size=17), 
            axis.text.y = element_text(size = 17),
            #legend.key = element_rect(color = "black"),
            legend.text = element_text(size = 15),
            legend.title = element_text(size = 18),
            #legend.position = "top",
            axis.title.y = element_text(size = rel(1.5)),
            axis.title.x = element_text(size = rel(1.5)),
            legend.title = element_text(size = rel(2)),
            plot.title = element_text(size = rel(2))
        ) + labs(title="Comparison between two nominees", x = "Players", y = "PositionWise Vote Count") + 
        geom_text(aes(y=value/2, label=value), position = position_dodge(width=1), size = 5) + 
        scale_y_continuous(breaks=seq(0, 350, 25)) + 
        scale_fill_brewer("Vote\nPositions", palette = "Set1")
```

*** {name: right}

```{r echo=FALSE, message=FALSE}
vote_group <- c("First", "Second", "Third")
vote_value_vec <- playerwise_men[playerwise_men$player_name == "Neymar", ]
vote_value <- as.numeric(as.vector(vote_value_vec[,2:4]))
r_data <- data.frame(vote_group = vote_group, vote_value = vote_value)
ggplot(r_data, aes(x=vote_group, y = vote_value, fill = vote_group)) + 
        geom_bar(stat="identity", color="black") + 
        geom_text(aes(y=vote_value/2, label = vote_value), size = 8) +
        theme_bw() +
        theme(
            axis.text.x = element_text(size=17), 
            axis.text.y = element_text(size = 17),
            #legend.key = element_rect(color = "black"),
            legend.text = element_text(size = 15),
            legend.title = element_text(size = 18),
            #legend.position = "top",
            axis.title.y = element_text(size = rel(1.5)),
            axis.title.x = element_text(size = rel(1.5)),
            legend.title = element_text(size = rel(2)),
            plot.title = element_text(size = rel(2))
        ) +
        scale_fill_brewer("Vote\nPositions", palette = "Set1") +
        scale_y_continuous(breaks = seq(0, 475, 25)) +
        labs(title = "Vote Distribution for Neymar", x = "Vote Positions", y = "Vote Count")
```

